Programming Assignment 2

### 2015-04-02 paper.tex
Corrected BAM implementation.

\subsection{Skyler "Scrub" Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

@@

\subsection{William Fong}
\subsubsection{Programming}
William worked to creat the Max layer of the Hamming/Max network and coordinate 
inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.

>>>>

\subsection{Skyler "Scrub on the Frub" Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

@@

\subsection{William Fong}
\subsubsection{Programming}
William worked to create the Max layer of the Hamming/Max network and coordinate 
inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.
